Generalized Tractability

### 2023-04-13 Older_versions/GeneralizedTractability_230310.tex
Updates from Overleaf

Let $T: (0,\infty) \times \naturals \times [0,\infty) \times [0,\infty)\Rightarrow [1,\infty)$. Suppose we have $T$-$(s,t)$- weak tractability, such that
\[
 \lim_{d+\varepsilon^{-1}\rightarrow\infty} \frac{\log \max(1,n(\varepsilon,d))}{d^t +(\max(1,\varepsilon^{-1}))^s} =0.
\]
Then Theorem \ref{thm:weak} yields the iff-condition
\[
\sup_{d\in\naturals} \sigma (c,d,s,\vp) \exp\left(-c\, T(0,d^t,\vp)\right)<\infty
\]
where $\sigma (c,d,s,\vp) = $

@@

\begin{definition}[$T$-Quasi-polynomial tractability]
We say that the problem is \emph{$T$- quasi-polynomial tractable} if there exists positive $C_{\vp}$ such that
   \[ n(\varepsilon,d)\leq C_{\vp}\exp\{(T(0,d,\vp))(T(\varepsilon^{-1},1,\vp)\}\]
  % \[ n(\varepsilon,d)\leq C_{\vp}\exp\{(T(\varepsilon^{-1},d,\vp)\}\]
\end{definition}

\begin{theorem}\label{thm:qpt}
A problem is $T$-quasi-polynomial tractable iff there exists $\vp \in [\vzero, \boldsymbol{\infty})$ such that
\begin{equation}\label{thmqpt}
M_{\vp} := \sup_{d\in\mathbb{N}}\sum_{i=1}^\infty \frac{1}{T(\lambda_{i,d}^{-1},d,\vp)}
<\infty
\end{equation}
%where $\Bar{p} = -p(1+\log(T(0,d,\vp))$.
%If it holds then 
%\[n(\varepsilon,d)\leq 1+T(0,d^\tau,\vp)+ T(0,d^\tau,\vp)T(\varepsilon^{-1},1,\vp)\]
\end{theorem}
\begin{proof}
\textbf{Necessity Condition:}\\
Suppose that we have $T$-quasi-polynomial tractability, i.e., for some $\vp\geq 0$, there exists positive $C_{\vp}$ such that
\[\comp(\varepsilon,d)\le C_{\vp}\exp\{(T(0,d,\vp)(T(\varepsilon^{-1},1,\vp))\}\quad\quad \forall\varepsilon >0, d\in \mathbb{N}\] 
%\[\comp(\varepsilon,d)\le C_{\vp}\exp\{T(\varepsilon^{-1},d,\vp)\}\quad\quad \forall\varepsilon >0, d\in \mathbb{N}\] 
Since $\lambda_{i,d}$ are non-increasing, we have
\[
\lambda_{\left\lfloor C_{\vp}\exp\{(T(0,d,\vp)(T(\varepsilon^{-1},1,\vp))\}\right\rfloor+1,d}\leq \varepsilon^2
\]
Given that the estimate holds for all $\varepsilon> 0$, we assume that $\varepsilon \in (0, 1]$.\\

If we vary $\varepsilon\in (0,1]$, we have that
\[
j(\varepsilon,d,\vp) = \left\lfloor C_{\vp}\exp\{(T(0,d,\vp)(T(\varepsilon^{-1},1,\vp))\}\right\rfloor+1
\] which attains the values $j = j_d,j_{d+1},\dots$, where
\[
j(\infty,d,\vp)=j_d = \lfloor C_{\vp}\exp\{ T(0,d,\vp)\}\rfloor + 1
\]
Furthermore, we have
\[j \leq C_{\vp}\exp\{(T(0,d,\vp)(T(\varepsilon^{-1},1,\vp))\}+1 \leq C_{\vp}\exp\{(T(0,d,\vp)(T(\lambda^{-1}_{j,d},1,\vp))\}+1 \quad \forall j \geq j_d \]
This implies that for $\tau>1$, we have
\[
\left(\frac{j-1}{C_{\vp}}\right)^{\tau/T(0,d,\vp)} \leq \exp\{T(\lambda^{-1}_{j,d},1,\vp)\}
\]
\[
\exp\{-\tau T(\lambda^{-1}_{j,d},1,\vp\} \leq \left(\frac{C_{\vp}}{j-1}\right)^{\tau/T(0,d,\vp)}\Rightarrow
\exp\{-\tau T(\lambda^{-1}_{j,d},1,\vp)(T(0,d,\vp)\} \leq C_{\vp}^\tau (j-1)^{-\tau}
\]

%\[\frac{1}{T(\lambda_{i,d}^{-1},d,\vp)} \leq \frac{K_{\vp,\tau}}{\left(\log\frac{j-1}{C_{\vp}}\right)^\tau}\]

\textbf{Sufficient condition:} Suppose that (\ref{}) holds for some $\vp \geq 0$. We need to show that for some $C_{\vp}>0$ we have 
\[
\text{comp}(\varepsilon,d) \leq C_{\vp}\exp\{T(0,d,\vp)T(\varepsilon^{-1},1,\vp)\} \quad \forall \varepsilon > , d \in \mathbb{N}
\] Let
\end{proof}

>>>>

Let $T: (0,\infty) \times \naturals \times [0,\infty) \times [0,\infty)\Rightarrow [1,\infty)$. Suppose we have $T$-$(s,t)$- weak tractability, such that
\[
 \lim_{d+\varepsilon^{-1}\rightarrow\infty} \frac{\log \max(1,n(\varepsilon,d))}{d^t +(\max(1,\varepsilon^{-1}))^s} =0.
\]
Then Theorem \ref{thm:weak} yields the iff-condition
\[
\sup_{d\in\naturals} \sigma (c,d,s,\vp) \exp\left(-cd^t\right)<\infty
\]
where $\displaystyle\sigma (c,d,s,\vp) =\sum_{i=1}^\infty \exp\left(-c\left(\lambda^{-1}_{i,d}\right)^{s/2}\right) $

@@

\begin{definition}[$T$-Quasi-polynomial tractability]
We say that the problem is \emph{$T$- quasi-polynomial tractable} if there exists positive $C_{\vp}$ such that
 %  \[ n(\varepsilon,d)\leq C_{\vp}\exp\{(T(0,d,\vp))(T(\varepsilon^{-1},1,\vp)\}\]
  \[ n(\varepsilon,d)\leq C_{\vp}\exp\{(T(\varepsilon^{-1},d,\vp)\}\]
\end{definition}

\begin{theorem}\label{thm:qpt}
A problem is $T$-quasi-polynomial tractable iff there exists $\vp \in [\vzero, \boldsymbol{\infty})$ such that
\begin{equation}\label{thmqpt}
M_{\vp} := \sup_{d\in\mathbb{N}}\sum_{i=1}^\infty \left[\frac{1}{T(\lambda_{i,d}^{-1},d,\vp)}\right]^{T(0,d,\vp)}
<\infty
\end{equation}
%where $\Bar{p} = -p(1+\log(T(0,d,\vp))$.
%If it holds then 
%\[n(\varepsilon,d)\leq 1+T(0,d^\tau,\vp)+ T(0,d^\tau,\vp)T(\varepsilon^{-1},1,\vp)\]
\end{theorem}
\begin{proof}
\textbf{Necessity Condition:}\\
Suppose that we have $T$-quasi-polynomial tractability, i.e., for some $\vp\geq 0$, there exists positive $C_{\vp}$ such that
%\[\comp(\varepsilon,d)\le C_{\vp}\exp\{(T(0,d,\vp)(T(\varepsilon^{-1},1,\vp))\}\quad\quad \forall\varepsilon >0, d\in \mathbb{N}\] 
\[\comp(\varepsilon,d)\le C_{\vp}\exp\{(T(0,d,\vp))(T(\varepsilon^{-1},d,\vp))\}\quad\quad \forall\varepsilon >0, d\in \mathbb{N}\] 
Since $\lambda_{i,d}$ are non-increasing, we have
%\[\lambda_{\left\lfloor C_{\vp}\exp\{T(\varepsilon^{-1},d,\vp)\}\right\rfloor+1,d}\leq \varepsilon^2\]
\[
\lambda_{\left\lfloor C_{\vp}\exp\{(T(0,d,\vp))(T(\varepsilon^{-1},d,\vp))\}\right\rfloor+1,d}\leq \varepsilon
\]
Given that the estimate holds for all $\varepsilon> 0$, we assume that $\varepsilon \in (0, 1]$.\\

If we vary $\varepsilon\in (0,1]$, we have that
\[
j(\varepsilon,d,\vp) = \left\lfloor C_{\vp}\exp\{(T(0,d,\vp))(T(\varepsilon^{-1},d,\vp))\}\}\right\rfloor+1
\] which attains the values $j = j_d,j_{d+1},\dots$, where
\[
j(\infty,d,\vp)=j_d = \lfloor C_{\vp}\exp\{(T(0,d,\vp))T(0,d,\vp)\}\rfloor + 1
\]
Furthermore, we have
\[j \leq C_{\vp}\exp\{(T(0,d,\vp))(T(\varepsilon^{-1},d,\vp)\}+1 \leq C_{\vp}\exp\{(T(0,d,\vp))(T(\lambda_{j,d}^{-1},d,\vp)\}+1 \quad \forall j \geq j_d \]
This implies that for $\tau>1$, we have
\[
(j-1)^{\tau} \leq C_{\vp}\exp\{\tau(T(0,d,\vp)) (T(\lambda_{j,d}^{-1},d,\vp)\}
\]
This implies
\[
\exp\{-\tau(T(0,d,\vp))( T(\lambda_{j,d}^{-1},d,\vp) \leq \frac{C_{\vp}}{(j-1)^\tau}
\]
We can get
\[
T(\lambda_{i,d},d,\vp))^{-\tau T(0,d,\vp)}\leq C_{\tau,\vp}\frac{1}{(j-1)^\tau} 
\]provided $T(\lambda_{i,d},d,\vp)\geq e$. Therefore, we get
\[
\sum_{i=1}^\infty T(\lambda_{i,d},d,\vp))^{-\tau T(0,d,\vp)} \leq C_{\tau,\vp}\sum_{i=1}^\infty \frac{1}{(j-1)^\tau}
< \infty\]
%\[\frac{1}{T(\lambda_{i,d}^{-1},d,\vp)} \leq \frac{K_{\vp,\tau}}{\left(\log\frac{j-1}{C_{\vp}}\right)^\tau}\]
This yields \eqref{thmqpt}.\\
\textbf{Sufficient condition:} Suppose that (\ref{thmqpt}) holds for some $\vp \geq 0$. We need to show that for some $C_{\vp}>0$ we have 
\[
\text{comp}(\varepsilon,d) \leq C_{\vp}\exp\{(T(0,d,\vp))(T(\varepsilon^{-1},d,\vp)\} \quad \forall \varepsilon > , d \in \mathbb{N}
\] Given that $\lambda_{i,d}$ are non-increasing, it follows that $T$ is increasing in its arguments, hence we have the following arguments from previous theorems, i.e.,
\[
\text{comp}(\varepsilon,d) \leq \left(T(\varepsilon^{-1},d,\vp)\right)^{T(0,d,\vp)}\sum_{j=1}^\infty\left[\frac{1}{T(\lambda^{-1}_{j,d},d,\vp)}\right]^{T(0,d,\vp)}
\]
Now, we have the following upper bound on the complexity as follows
\begin{align*}
    \comp(\varepsilon,d) &\leq T(\varepsilon^{-1},d,\vp)^{T(0,d,\vp)}\sum_{j=1}^\infty\left[\frac{1}{T(\lambda^{-1}_{j,d},d,\vp)}\right]^{T(0,d,\vp)}\\
    &\leq T(\varepsilon^{-1},d,\vp)^{T(0,d,\vp)}\left[\sum_{j=1}^{C_{\vp}-1}\left[\frac{1}{T(\lambda^{-1}_{j,d},d,\vp)}\right]^{T(0,d,\vp)} + \sum_{j=C_{\vp}}^\infty\left[ \frac{1}{T(\lambda_{j,d}^{-1},d,\vp)}\right]^{T(0,d,\vp)}\right]\\
     & \le T(\varepsilon^{-1},d,\vp)^{T(0,d,\vp)}\left[ \left[\frac{C_{\vp}-1}{T(\lambda_{\max}^{-1},d,\vp)}\right]^{T(0,d,\vp)} + M_{\vp}\right]
        \qquad \text{by \eqref{thmqpt}} \\
       & \le T(\varepsilon^{-1},d,\vp)^{T(0,d,\vp)}\left[(C_{\vp})^{T(0,d,\vp)} + M_{\vp}\right]\\ 
       & \le \left(C_{\vp}\,T(\varepsilon^{-1},d,\vp)\right)^{T(0,d,\vp)} + M_{\vp}\, T(\varepsilon^{-1},d,\vp)^{T(0,d,\vp)}\\
       & \le C_{\vp}\,T(\varepsilon^{-1},d,\vp)^{T(0,d,\vp)}
\end{align*}
%It follows that we have $T$-quasi-polynomial tractability.
\end{proof}
\kachi{To do: Find an example for this case.}
